About

### 2020-08-05 analysis/about.Rmd
update about.Rmd

    - high-dimensional data handling
    - feature selection
    - machine-learning
    - ecology

@@

[![Build Status](https://travis-ci.org/pat-s/paper_hyperspectral.svg?branch=master)](https://travis-ci.org/pat-s/paper_hyperspectral)

@@

The R library of this project is managed by [packrat](https://rstudio.github.io/packrat/).
This makes sure that the exact same package versions are used when recreating the project.
When calling `packrat::restore()`, all required packages will be installed with their specific version.

Please note that this project was built with R version 3.5.2 on a Debian 9 operating system.
The packrat packages from this project **are not compatible with R versions prior version 3.5.0.**
For reproducibility, it is recommended to replicate the analysis using the included Dockerfile.
Instructions can be found [ħere](https://github.com/pat-s/paper_hyperspectral#docker).
(In general, it should be possible to reproduce the analysis on any other operating system.)

@@

```sh
git clone git@github.com:pat-s/paper_hyperspectral.git
```

@@

```{r README-1, eval = FALSE}
packrat::restore()
r_make()
```

@@

* The [issues tracker](https://github.com/pat-s/paper_hyperspectral/issues) is the place to report problems or ask questions

* See the repository [history](https://github.com/pat-s/paper_hyperspectral/commits/master) for a fine-grained view of progress and changes.

@@

# Literature

- What to do first (Feature selection or tuning): https://datascience.stackexchange.com/a/19778/24475
- Hastie, T., Friedman, J., & Tibshirani, R. (2001). The Elements of Statistical Learning. Springer New York. https://doi.org/10.1007/978-0-387-21606-5 (Kapitel 16)
- FSel algs overview: http://featureselection.asu.edu/algorithms.php
- De Jay, N., Papillon-Cavanagh, S., Olsen, C., El-Hachem, N., Bontempi, G., & Haibe-Kains, B. (2013). mRMRe: an R package for parallelized mRMR ensemble feature selection. Bioinformatics, 29(18), 2365–2368. https://doi.org/10/f48vxc
- Drotár, P., Gazda, J., & Smékal, Z. (2015). An experimental comparison of feature selection methods on two-class biomedical datasets. Computers in Biology and Medicine, 66, 1–10. https://doi.org/10/f72ttc
- Drotár, P., Šimoňák, S., Pietriková, E., Chovanec, M., Chovancová, E., Ádám, N., … Biňas, M. (2017). Comparison of Filter Techniques for Two-Step Feature Selection. COMPUTING AND INFORMATICS, 36(3), 597–617. https://doi.org/10/gbntp7
- Drotár, P., Gazda, M., & Gazda, J. (2017). Heterogeneous ensemble feature selection based on weighted Borda count. In 2017 9th International Conference on Information Technology and Electrical Engineering (ICITEE) (pp. 1–4). https://doi.org/10.1109/ICITEED.2017.8250495
- Nie, F., Huang, H., Cai, X., & Ding, C. H. (2010). Efficient and Robust Feature Selection via Joint \mathscrl2,1-Norms Minimization. In J. D. Lafferty, C. K. I. Williams, J. Shawe-Taylor, R. S. Zemel, & A. Culotta (Eds.), Advances in Neural Information Processing Systems 23 (pp. 1813–1821). Curran Associates, Inc. Retrieved from http://papers.nips.cc/paper/3988-efficient-and-robust-feature-selection-via-joint-l21-norms-minimization.pdf

>>>>

  - hyperspectral imagery
  - forest health monitoring
  - machine learning
  - feature selection
  - feature effects
  - model comparison
  - filter
  - imaging spectroscopy

@@

@@

The R library of this project is managed by [renv](https://rstudio.github.io/renv/index.html).
This makes sure that the exact same package versions are used when recreating the project.
When calling `renv::restore()`, all required packages will be installed with their specific version.

Please note that this project was built with R version 3.6.1 on a CentOS 7 operating system.
Some packages from this project **are not compatible with R versions prior version 3.6.0.**

@@

```sh
git clone https://github.com/pat-s/2019-feature-selection.git
```

@@

```{r README-1, eval = FALSE}
renv::restore()
r_make()
```

@@

@@
